Worflow

### 2017-06-11 R/workflow.Rmd
version control for zinbwave

```{r options, echo=FALSE, results="hide",message=FALSE, error=FALSE, include=FALSE, autodep=TRUE}
knitr::opts_chunk$set(fig.align="center", cache=TRUE, error=FALSE, message=FALSE, warning=TRUE)
#bioconductor:
library(scRNAseq)
library(scone)
library(clusterExperiment)
#github
library(zinbwave)
library(slingshot)
#CRAN
library(ggplot2)
library(gplots)
library(magrittr)
library(matrixStats)
library(Rtsne)
library(RColorBrewer)
library(digest)
library(rARPACK)
set.seed(20)
if(packageVersion("clusterExperiment")<'1.3.0.9009') stop("must have current develop version to avoid bugs")
```

@@

EAP: if we are going to ultimately use these functions, it would be good to add them to the package for zinbwave.

FP: yes, I agree. Davide, we wait for zinbwave to be on bioconductor before to push changes, right?

```{r residuals}
compute.zinb.loglik <- function(Y, zinb){
  mu = t(getMu(zinb)) 
  theta = getTheta(zinb)
  theta_mat = matrix(rep(theta, ncol(Y), ncol = ncol(Y)))
  pi = t(getPi(zinb))
  log( pi * (Y == 0) + (1 - pi) * dnbinom(Y, size = theta, mu = mu) )
}

compute.deviance.residuals <- function(Y, zinb){
  mu_hat = t(getMu(zinb)) 
  pi_hat = t(getPi(zinb)) 
  Y_hat = (1 - pi_hat) * mu_hat
  ll = compute.zinb.loglik(Y, zinb)
  sign = 1*(Y - Y_hat > 0)
  sign[sign == 0] = -1
  sign * sqrt(-2 * ll)
}
```

@@

```{r}
fn0 <- '../data/zinb_k0_batch.rda'
if (runZinb & !file.exists(fn0)){
  mod <- model.matrix( ~ batch)
  print(system.time(zinb0 <- zinbFit(core, ncores = NCORES,
                                     K = 0, X = mod)))
  save(zinb0, file = fn0)
}else{
  load(fn0)
}

fn50 <- '../data/zinb_k50_batch.rda'
if (runZinb & !file.exists(fn50)){
  mod <- model.matrix( ~ batch)
  print(system.time(zinb50 <- zinbFit(core, ncores = NCORES,
                                      K = 50, X = mod)))
  save(zinb50, file = fn50)
}else{
  load(fn50)
}
```

@@

```{r}
res <- compute.deviance.residuals(core, zinb0)
res[1:3,1:3]
```

>>>>

```{r options, echo=FALSE, results="hide",message=FALSE, error=FALSE, include=FALSE, autodep=TRUE}
knitr::opts_chunk$set(fig.align="center", cache=TRUE, error=FALSE, message=FALSE, warning=TRUE)
#bioconductor:
library(scRNAseq)
library(scone)
library(clusterExperiment)
#github
library(zinbwave)
library(slingshot)
#CRAN
library(ggplot2)
library(gplots)
library(magrittr)
library(matrixStats)
library(Rtsne)
library(RColorBrewer)
library(digest)
library(rARPACK)
set.seed(20)
if(packageVersion("clusterExperiment")<'1.3.0.9008') stop("must have current develop version to avoid bugs")
if(packageVersion("zinbwave")<'0.99.4.1') stop("must have current develop version to avoid bugs")
```

FP: Elizabeth, I could not install the last version 1.3.0.9009 of clusterExperiment. The error is

checking DESCRIPTION meta-information ... ERROR
Malformed Depends or Suggests or Imports or Enhances field.
Offending entries:
  MAST
BiocStyle
Entries must be names of packages optionally followed by '<=' or '>=',
white space, and a valid version number in parentheses.

@@

@@

```{r}
fn <- '../data/zinb_batch.rda'
if (runZinb & !file.exists(fn)){
  mod <- model.matrix( ~ batch)
  print(system.time(zinb <- zinbDimRed(se, K = 50, X = mod, residuals = T,
                                       normalizedValues = T)))
  save(zinb, file = fn)
}else{
  load(fn)
}
```

@@

```{r}
res <- computeDevianceResiduals(zinb, core)
res[1:3,1:3]
```
